SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-02-16 scipy-1.0/paper.tex
ENH: intro: "Despite its success" doesn't belong here This is sort of negative, so I don't think it really belongs in the introduction. Perhaps it would fit somewhere that describes challenges ahead.
ENH: intro: part -> piece of the puzzle

Despite its success, SciPy still faces challenges:
a low ``bus factor''---meaning that the entire project depends on a small number of
active contributors---being perhaps the most serious.

In the background section that follows, we capture a selective history
of some milestones and important events in the growth of SciPy.
Despite what we might highlight here, it is important to understand
that a project like SciPy is only possible because of the
contributions of very many contributors---too many to mention
individually, but each bringing an important part to the puzzle.

>>>>

% Despite its success, SciPy still faces challenges:
% a low ``bus factor''---meaning that the entire project depends on a small number of
% active contributors---being perhaps the most serious.

In the background section that follows, we capture a selective history
of some milestones and important events in the growth of SciPy.
Despite what we might highlight here, it is important to understand
that a project like SciPy is only possible because of the
contributions of very many contributors---too many to mention
individually, but each bringing an important piece to the puzzle.
